Article 8 : Electronic nose can sniff out which lung cancer patients will respond to immunotherapy

### 2020-03-14 _posts/2019-09-18-article-1/article-1.Rmd
correction articles

|                             |                                                                                                                                                                                                                                                                                                                                                                           |
| --------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                 | Medical College of Georgia at Augusta University (lead authors : Dr. Wei Xiao, Dr. Mumtaz Rojiani, Dr. Amyn Rojiani)                                                                                                                                                                                                                                                      |
| Published in                | ScienceDaily, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
| General topic               | The way cancerous cells avoid apoptosis (non-small cell lung cancer)                                                                                                                                                                                                                                                                                                      |
| Procedure/what was examined | goal was to evidence link between TIMP-1 and resistance to chemotherapy + they used two drugs to destroy TIMP-1, then also destroy it by antibodies + added TIMP-1 to see the effect, then added IL-6  + STAT3 : regulator of gene activity (cell growth,division,  movement, apoptosis)                                                                                  |
| Conclusions/discovery       | high rate of TIMP-1 increases rate of IL-6 which make cells avoid apoptosis + low rate of TIMP-1 => lower rate of IL-6 => more apoptosis of cancerous cells => higher survival rate for patients + adding IL-6 has no real effect on apoptosis + remaining cancerous cells are more resistant + high level of IL-6 => STAT3 moves to nucleus => helps to reduce apoptosis |
| Remaining questions         | Does STAT3 activate more TIMP-1 production ?                                                                                                                                                                                                                                                                                                                              |

>>>>

|                             |                                                                                                                                                                                                                                                                                                                                                                           |
| --------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                 | Medical College of Georgia at Augusta University (lead authors : Dr. Wei Xiao, Dr. Mumtaz Rojiani, Dr. Amyn Rojiani)                                                                                                                                                                                                                                                      |
| Published in                | Cancers, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
| General topic               | The way cancerous cells avoid apoptosis (non-small cell lung cancer)                                                                                                                                                                                                                                                                                                      |
| Procedure/what was examined | goal was to evidence link between TIMP-1 and resistance to chemotherapy + they used two drugs to destroy TIMP-1, then also destroy it by antibodies + added TIMP-1 to see the effect, then added IL-6  + STAT3 : regulator of gene activity (cell growth,division,  movement, apoptosis)                                                                                  |
| Conclusions/discovery       | high rate of TIMP-1 increases rate of IL-6 which make cells avoid apoptosis + low rate of TIMP-1 => lower rate of IL-6 => more apoptosis of cancerous cells => higher survival rate for patients + adding IL-6 has no real effect on apoptosis + remaining cancerous cells are more resistant + high level of IL-6 => STAT3 moves to nucleus => helps to reduce apoptosis |
| Remaining questions         | Does STAT3 activate more TIMP-1 production ?                                                                                                                                                                                                                                                                                                                              |

### 2020-03-14 _posts/2019-10-18-article-2/article-2.Rmd
correction articles

|                               |                                                                                                                                                                                                                                                                                                                                                                                                             |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | (two studies) 1) Michele Pagano (New York University School of Medicine) 2) Martin Bergö (Karolinska Institutet in Stockholm)                                                                                                                                                                                                                                                                               |
| General topic                 | the bad effect of antioxidants when you have lung caner                                                                                                                                                                                                                                                                                                                                                     |
| Published in                  | Science News, 27 June 2019                                                                                                                                                                                                                                                                                                                                                                                  |
| Procedure / what was examined |  experiments on mice and humans  1) antioxidant- producing genes + effect of antioxidants 2) antioxidant // dietary supplement                                                                                                                                                                                                                                                                              |
| Conclusion / discovery        | 1) antioxidants protect cancerous cells + help to accumulate protein Bach1 => more glycolysis => encourage metastasis + cancerous cells have mutations in genes producing antioxidants => higher production => production of Nrf2 => highe rate og Ho1 => protection from free radicals 2) higher rates of Bach1 protein + Bach1 activate genes that accelerate glucose uptake and glycolysis => metastases |
| Remaining questions           | finding drugs to inhibit Ho1, Bach1 and decrease glycolysis + giving inhibitors used to treat porphyrias to patients affected by lung cancer + Why some lung cancer metastasizes and other don't ? + Do these proteins also play a role in other cancers ?                                                                                                                                                  |

>>>>

|                               |                                                                                                                                                                                                                                                                                                                                                                                                             |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | (two studies) 1) Michele Pagano (New York University School of Medicine) 2) Martin Bergö (Karolinska Institutet in Stockholm)                                                                                                                                                                                                                                                                               |
| General topic                 | the bad effect of antioxidants when you have lung caner                                                                                                                                                                                                                                                                                                                                                     |
| Published in                  | Cell, 27 June 2019                                                                                                                                                                                                                                                                                                                                                                                  |
| Procedure / what was examined |  experiments on mice and humans  1) antioxidant- producing genes + effect of antioxidants 2) antioxidant // dietary supplement                                                                                                                                                                                                                                                                              |
| Conclusion / discovery        | 1) antioxidants protect cancerous cells + help to accumulate protein Bach1 => more glycolysis => encourage metastasis + cancerous cells have mutations in genes producing antioxidants => higher production => production of Nrf2 => highe rate og Ho1 => protection from free radicals 2) higher rates of Bach1 protein + Bach1 activate genes that accelerate glucose uptake and glycolysis => metastases |
| Remaining questions           | finding drugs to inhibit Ho1, Bach1 and decrease glycolysis + giving inhibitors used to treat porphyrias to patients affected by lung cancer + Why some lung cancer metastasizes and other don't ? + Do these proteins also play a role in other cancers ?                                                                                                                                                  |

### 2020-03-14 _posts/2019-11-02-article-3/article-3.Rmd
correction titre article 3
correction articles

## Soruce of the article

@@

|                               |                                                                                                                                                                                                 |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Prof Frank Sullivan                                                                                                                                                                             |
| General topic                 | detection of lung cancer                                                                                                                                                                        |
| Published in                  | BBC, 10 September 2019 (presented a few days earlier in World Conference of Lung cancer in Barcelona)                                                                                           |
| Procedure / what was examined | trial on more than 12,000 people who were at risk (smokers and former smokers, between 50 and 75 years old) : blood test + CT scans (= computed tomography scans) + detection of autoantibodies |
| Conclusion / discovery        | detecting lung cancer at an early stage is possible : lower death rates and lower cost of treatment                                                                                             |
| Remaining questions           |                                                                                                                                                                                                 |

>>>>

## Source of the article

@@

|                               |                                                                                                                                                                                                 |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Prof Frank Sullivan                                                                                                                                                                             |
| General topic                 | detection of lung cancer                                                                                                                                                                        |
| Published in                  | World Conference on Lung Cancer, 9 September 2019                                                                                            |
| Procedure / what was examined | trial on more than 12,000 people who were at risk (smokers and former smokers, between 50 and 75 years old) : blood test + CT scans (= computed tomography scans) + detection of autoantibodies |
| Conclusion / discovery        | detecting lung cancer at an early stage is possible : lower death rates and lower cost of treatment                                                                                             |
| Remaining questions           |                                                                                                                                                                                                 |

### 2020-03-14 _posts/2019-11-29-article-4/article-4.Rmd
modif. article 4 + test logo
correction articles

@@

|                               |                                                                                                                                                                                                              |
| ----------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------ |
| Researchers                   | Professor Reuben Shaw, Salk Institute                                                                                                                                                                        |
| General topic                 |                                                                                                                                                                                                              |
| Published in                  | Science Daily, on 26 July 2019                                                                                                                                                                               |
| Procedure / what was examined | inactive gene LKB1 => cancer development + enzymes involved in inflammation / 12 potential enzymes that could suppress effect of LKB1 -> CRISPR + genetic analysis to inactivate each enzyme (+combinations) |
| Conclusion / discovery        | LKB1 <-> 2 enzymes (SIK1 and SIK3) that blocks tumor growth : SIK1 inactivated <-> increased tumor growth, SIK3 inactivated <-> tumor grows more aggressively => inflammation plays a role in lung cancer    |
| Remaining questions           | How do these kinase-driven changes in inflammation cause lung tumor growth ?                                                                                                                                 |

>>>>

Word count : 714

@@

|                               |                                                                                                                                                                                                              |
| ----------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------ |
| Researchers                   | Professor Reuben Shaw, Salk Institute                                                                                                                                                                        |
| General topic                 | Inactivating LKB1 triggers cancer development                                                                                                                                                                                                             |
| Published in                  | Cancer Discovery, on 26 July 2019                                                                                                                                                                               |
| Procedure / what was examined | inactive gene LKB1 => cancer development + enzymes involved in inflammation / 12 potential enzymes that could suppress effect of LKB1 -> CRISPR + genetic analysis to inactivate each enzyme (+combinations) |
| Conclusion / discovery        | LKB1 <-> 2 enzymes (SIK1 and SIK3) that blocks tumor growth : SIK1 inactivated <-> increased tumor growth, SIK3 inactivated <-> tumor grows more aggressively => inflammation plays a role in lung cancer    |
| Remaining questions           | How do these kinase-driven changes in inflammation cause lung tumor growth ?                                                                                                                                 |

### 2020-03-14 _posts/2020-02-14-article-6/article-6.Rmd
correction articles

|                               |                                                                                                                                                                                                         |
| ----------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Jennifer Cochran, Alejandro Sweet-Cordero, Jun Kim and Cesar Marquez (Stanford and UC-San Francisco)                                                                                                    |
| General topic                 | Creating a decoy protein to stop a chain reaction (leading to the spread of cancer)                                                                                                                     |
| Published in                  | Science Daily, 7 November 2019                                                                                                                                                                          |
| Procedure / what was examined | In 1 tpye of non-small cell lung cancer : mutation in KRAS gene -> CLCF1 binds to 3 receptors (+activation) and is released by fibroblasts (induction by cancerous epithelial cells) -> mechanism ?     |
| Conclusion / discovery        | CLCF1 first binds to CNTFR -> this complex attracts the other receptors (gp130 and LIFR) => more energy for the tumor -> making a decoy receptor similar to CNTFR (but inactive) -> tested on mice : OK |
| Remaining questions           | Will it work on humans ?                                                                                                                                                                                |

>>>>

|                               |                                                                                                                                                                                                         |
| ----------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Jennifer Cochran, Alejandro Sweet-Cordero, Jun Kim and Cesar Marquez (Stanford and UC-San Francisco)                                                                                                    |
| General topic                 | Creating a decoy protein to stop a chain reaction (leading to the spread of cancer)                                                                                                                     |
| Published in                  | Nature Medicine, 7 November 2019                                                                                                                                                                          |
| Procedure / what was examined | In 1 tpye of non-small cell lung cancer : mutation in KRAS gene -> CLCF1 binds to 3 receptors (+activation) and is released by fibroblasts (induction by cancerous epithelial cells) -> mechanism ?     |
| Conclusion / discovery        | CLCF1 first binds to CNTFR -> this complex attracts the other receptors (gp130 and LIFR) => more energy for the tumor -> making a decoy receptor similar to CNTFR (but inactive) -> tested on mice : OK |
| Remaining questions           | Will it work on humans ?                                                                                                                                                                                |

### 2020-03-14 _posts/2020-02-29-article-7/article-7.Rmd
correction articles

|                               |                                                                                                                                                                                                                                                       |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Dawen Zhao (Wake Forest School of Medicine)                                                                                                                                                                                                           |
| General topic                 | Inhalable nano-particles to treat lung cancer                                                                                                                                                                                                         |
| Published in                  | Science Daily, 14 November 2019                                                                                                                                                                                                                       |
| Procedure / what was examined | mice, inhalable particles (immunotherapy; non-invasive, access not only to the surface) -> taken up by APC cells => activation of immune response + radiation therapy; injection of immunomodulators not so efficient (<-> only surface of the tumor) |
| Conclusion / discovery        | regression of tumors + longer survival; elimination of tumors in some cases                                                                                                                                                                           |
| Remaining questions           | /                                                                                                                                                                                                                                                     |

>>>>

|                               |                                                                                                                                                                                                                                                       |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Dawen Zhao (Wake Forest School of Medicine)                                                                                                                                                                                                           |
| General topic                 | Inhalable nano-particles to treat lung cancer                                                                                                                                                                                                         |
| Published in                  | Nature Communications, 14 November 2019                                                                                                                                                                                                                       |
| Procedure / what was examined | mice, inhalable particles (immunotherapy; non-invasive, access not only to the surface) -> taken up by APC cells => activation of immune response + radiation therapy; injection of immunomodulators not so efficient (<-> only surface of the tumor) |
| Conclusion / discovery        | regression of tumors + longer survival; elimination of tumors in some cases                                                                                                                                                                           |
| Remaining questions           | /                                                                                                                                                                                                                                                     |

### 2020-03-14 _posts/2020-03-13-article-8/article-8.Rmd
correction articles

|                               |                                                                                                                                                                                                                |
| ----------------------------- | -------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Michel van den Heuvel (Radboud University Medical Centre), Rianne de Vries (Amsterdam University Medical Centres) and Mirte Muller (The Netherlands Cancer Institute)                                          |
| General topic                 | An electronic nose detecting if patients will respond to immunotherapy                                                                                                                                         |
| Published in                  | Science Daily, 17 September 2019                                                                                                                                                                               |
| Procedure / what was examined | way to replace immunohistochemistry (invasive + need time) -> analysis of breath (detection of volatile organic compounds); tested on 143 patients -> then treatment and verification with the standard method |
| Conclusion / discovery        | distinction between responders  and non-responders : 85% accuracy (=> avoid side effects of immunotherapy when non-responders)                                                                                 |
| Remaining questions           | /                                                                                                                                                                                                              |

>>>>

|                               |                                                                                                                                                                                                                |
| ----------------------------- | -------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Michel van den Heuvel (Radboud University Medical Centre), Rianne de Vries (Amsterdam University Medical Centres) and Mirte Muller (The Netherlands Cancer Institute)                                          |
| General topic                 | An electronic nose detecting if patients will respond to immunotherapy                                                                                                                                         |
| Published in                  | Annals of Oncology, 17 September 2019                                                                                                                                                                               |
| Procedure / what was examined | way to replace immunohistochemistry (invasive + need time) -> analysis of breath (detection of volatile organic compounds); tested on 143 patients -> then treatment and verification with the standard method |
| Conclusion / discovery        | distinction between responders  and non-responders : 85% accuracy (=> avoid side effects of immunotherapy when non-responders)                                                                                 |
| Remaining questions           | /                                                                                                                                                                                                              |
